---
title: "Johnson-Strother Replication"
author: "Jake S. Truscott"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

js_test <- get(load("C:/Users/Jake Truscott/Desktop/JS_Test_FINAL.rdata"))

pai_diagnostic_retrieval <- function(output,
                                     diagnostic,
                                     type,
                                     variables = NULL,
                                     combine_plots = FALSE
){

  diagnostic_output <- output$diagnostics[[diagnostic]] #diagnostic = 'placebo', 'push', 'bootstrap'

  if (diagnostic == 'placebo'){

    if(output$parameters$outcome_type == 'Binomial'){
      title_label = ' Predictive Accuracy '
    } else {
      title_label = ' RMSE '
    }

    if (type == 'all'){

      full <- diagnostic_output$placebo_full
      x_label = full$labels$x
      x_label = gsub('\\n', '', x_label)
      y_label = full$labels$y
      y_label = gsub('\\n', '', y_label)
      CI <- diagnostic_output$placebo_CI
      bootstrap <- diagnostic_output$bootstrap_omit_information
      #title_label = full$labels$y
      #title_label = gsub('\\n', '', title_label)
      full$labels$x = NULL
      CI$labels$y = NULL
      CI$labels$x = NULL
      bootstrap$labels$x = NULL
      bootstrap$labels$y = NULL

      if (is.null(variables)){
        full = full
        CI = CI
        bootstrap = bootstrap
      } else {
        full = full %+% subset(full$data, var %in% variables)
        CI = CI %+% subset(CI$data, var %in% variables)
        bootstrap = bootstrap %+% subset(bootstrap$data, dropped_var %in% variables)
      } # If Variable(s) Declared

      full_figure <- list(full + theme(legend.position = 'top'))
      other_figures <- list(CI  + labs(title = paste0('Distribution of ', title_label, '\nFrom Placebo Shuffling')) + theme(plot.title = element_text(hjust = 0.5)),
                            bootstrap  + labs(title = paste0('Distribution of ', title_label, '\nAfter Dropping Information')) + theme(plot.title = element_text(hjust = 0.5)))
      temp_figure <- cowplot::plot_grid(plotlist = full_figure, align = 'v')
      other_figure <- cowplot::plot_grid(plotlist = other_figures, ncol = 2, align = 'v')

      diagnostic_retrieved <- cowplot::plot_grid(temp_figure, other_figure, ncol = 1, rel_heights = c(2.5, 2))

    } else if (type == 'figure'){

      if (is.null(variables)){
        diagnostic_retrieved <- diagnostic_output$placebo_full #Returns Full Placebo Figure
      } else {
        diagnostic_retrieved <- diagnostic_output$placebo_full %+% subset(diagnostic_output$placebo_full$data, var %in% variables) #Returns Placebo Figure Filtered by Var(s)
      } # If Variable(s) Declared

    } else if (type == 'bootstrap_drop_vars'){

      if (is.null(variables)){
        diagnostic_retrieved <- diagnostic_output$bootstrap_omit_information #Returns Full Placebo Figure
      } else {
        diagnostic_retrieved <- diagnostic_output$bootstrap_omit_information %+% subset(diagnostic_output$bootstrap_omit_information$data, var %in% variables) #Returns Placebo Figure Filtered by Var(s)
      } # If Variable(s) Declared


    } else if (type == 'placebo_confidence'){

      if (is.null(variables)){
        diagnostic_retrieved <- diagnostic_output$placebo_CI #Returns Full Placebo Figure
      } else {
        diagnostic_retrieved <- diagnostic_output$placebo_CI %+% subset(diagnostic_output$placebo_CI$data, var %in% variables) #Returns Placebo Figure Filtered by Var(s)
      } # If Variable(s) Declared

    } else {

      diagnostic_retrieved <- diagnostic_output$data #Returns Placebo Fit Data

    }



  } #If Diagnostic is 'Placebo' # all, figure, placebo_confidence, bootstrap_drop_var

  if (diagnostic == 'push'){

    diagnostic_retrieved = list() #Initialize Empty List

    if (!is.null(variables)){

      for (var in 1:length(variables)){

        temp_var = variables[var]

        retrieval_type = ifelse(type == 'data', 'linear_fit', 'linear_plot')

        temp_var = variables[var]
        temp_retrieval <- diagnostic_output[[temp_var]][[retrieval_type]]
        diagnostic_retrieved[[as.character(temp_var)]] <- temp_retrieval

      }

    } else {

      variables <- names(diagnostic_output)
      vars <- names(diagnostic_output) #Get Var Names from Diagnostic[['push']]

      for (var in 1:length(vars)){

        temp_var = vars[var]

        retrieval_type = ifelse(type == 'linear_fit', 'linear_fit', 'linear_plot')

        temp_retrieval <- diagnostic_output[[temp_var]][[retrieval_type]]
        diagnostic_retrieved[[as.character(temp_var)]] <- temp_retrieval

      } # Grab Figure or Fit for Each Var
    }  #If No Variables Declared - Return All

    if (combine_plots == TRUE){

      titles_vector = names(diagnostic_retrieved)

      diagnostic_figure_retrieved <- diagnostic_retrieved

      for (i in 1:length(diagnostic_retrieved)){
        diagnostic_figure_retrieved[[i]]$labels$x = ''
        diagnostic_figure_retrieved[[i]]$labels$y = ''

      } #Remove Legends

      for (i in seq_along(diagnostic_figure_retrieved)) {
        diagnostic_figure_retrieved[[i]] <- arrangeGrob(
          diagnostic_figure_retrieved[[i]],
          top = textGrob(titles_vector[i], gp = gpar(fontsize = 14))
        )
      } # Add Var-Level Titles


      diagnostic_retrieved <- cowplot::plot_grid(plotlist = diagnostic_figure_retrieved,
                                                 ncol = round(length(variables)/2, 0),
                                                 scale = 0.9) # Arrange plots on a grid


      diagnostic_retrieved <- diagnostic_retrieved +
        draw_label("Step", x=0.5, y=  0, vjust=-1, angle= 0) +
        draw_label("Predicted Accuracy", x=  0, y=0.5, vjust= 1, angle=90)

    } #If combine_plots = TRUE, Combine Them to Single Plot and Return Plot (Else, Return List of Figures)


  } #If Diagnostic is 'Push'

  if (diagnostic == 'bootstrap'){

    if (type == 'data'){
      diagnostic_retrieved <- diagnostic_output$bootstrap_output
    } #If Type is Bootstrap Data Output

    if (type == 'distribution'){
      diagnostic_retrieved <- diagnostic_output$bootstrap_distribution
    } # If Type is Distribution Figure

    if (type == 'figure'){

      if (is.null(variables)){
        bootstrap_vars = names(diagnostic_output$bootstrap_output[!names(diagnostic_output$bootstrap_output) %in% c('accuracy', 'bootstrap_id')])
      } else {
        bootstrap_vars = variables
      } # If Variables = NULL, Get Vars from Boostrap Output Data

      diagnostic_retrieved <- list() # Initialize Empty List for Figures

      for (var in 1:length(bootstrap_vars)){
        diagnostic_retrieved[[bootstrap_vars[var]]] <- diagnostic_output$variable_figures[[bootstrap_vars[var]]]

      } #Collect Figures by Var

      if (combine_plots == TRUE){

        g_legend <- function(a.gplot) {
          tmp <- ggplot_gtable(ggplot_build(a.gplot))
          leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
          legend <- tmp$grobs[[leg]]
          return(legend)
        } #Get Legend Function

        legend <- g_legend(diagnostic_retrieved[[1]]) #Get Legend from First Plot

        for (i in 1:length(diagnostic_retrieved)){
          temp_figure <-  diagnostic_retrieved[[i]] +  guides(shape = 'none', fill = 'none', colour = 'none')
          diagnostic_retrieved[[i]] <- temp_figure
        } #Remove Legends

        {

          x_label = diagnostic_retrieved[[1]]$labels$x
          y_label = diagnostic_retrieved[[1]]$labels$y

        } #Grab Labels

        temp_figure <- cowplot::plot_grid(plotlist = diagnostic_retrieved,
                                          label_x = x_label,
                                          label_y = y_label)

        legend_below <- cowplot::plot_grid(NULL, legend, nrow = 2, align = 'v')

        diagnostic_retrieved <- cowplot::plot_grid(temp_figure, legend_below, ncol = 1, rel_heights = c(4, 1))



      } #If combine_plots = TRUE, Combine Them to Single Plot and Return Plot (Else, Return List of Figures)

    } #If Type is Var Figure

  } #If Diagnostic = 'bootstrap'

  if (diagnostic == 'summary'){

    summary_diagnostics <- list()

    summary_diagnostics[['Performance Metrics']] <- data.frame(output$declared_model$results)
    importance <- varImp(output$declared_model)
    importance <- as.data.frame(importance$importance[1])
    names(importance) <- 'Importance'
    summary_diagnostics[['Variable Importance']] <- importance

    predictions <- predict(output$declared_model, newdata = output$parameters$test_set)

    if (output$parameters$outcome_type == 'Binomial'){
      true_labels <- data.frame(output$parameters$test_set)[[output$parameters$outcome]]
      true_labels <- as.factor(true_labels)
      predictions <- factor(predictions, levels = levels(true_labels))
      conf_matrix <- confusionMatrix(predictions, true_labels)
      summary_diagnostics[['Confusion Matrix']] <- conf_matrix
      summary_diagnostics['Precision'] <- conf_matrix$byClass["Precision"]
      summary_diagnostics['Recall'] <-  conf_matrix$byClass["Recall"]
      summary_diagnostics['F1'] <-  conf_matrix$byClass["F1"]

      #final_model <- output$declared_model
      #train_data <- data.frame(output$parameters$train_set, check.names = F)
      #trainPred <- predict(final_model, newdata = train_data)
      #in_sample_accuracy <- sum(trainPred == train_data$direction) / nrow(train_data)
      #summary_diagnostics['In-Sample Accuracy'] <- in_sample_accuracy


    } else {

      mse <- mean((data.frame(output$parameters$test_set)[[output$parameters$outcome]] - predictions)^2)
      rmse <- sqrt(mse)
      mae <- mean(abs(data.frame(output$parameters$test_set)[[output$parameters$outcome]] - predictions))

      summary_diagnostics[['Mean Squared Error (MSE)']] <- mse
      summary_diagnostics[['Root Mean Squared Error (RMSE)']] <- rmse
      summary_diagnostics[['Mean Absolute Error (MAE)']] <- mae
    }


    diagnostic_retrieved <- summary_diagnostics

  }

  return(diagnostic_retrieved)


}

```

```{r dependency libraries, include = FALSE}

require(caret)
require(dplyr)
require(stringr)
require(doParallel)
require(broom)
require(cowplot)
require(gridExtra)
require(grid)
require(foreign)

```


```{r PAI Function Main, eval = F}
pai <- function(data, 
                model = NULL, 
                outcome = NULL,
                predictors = NULL, 
                interactions = NULL, 
                drop_vars = NULL, 
                cores = NULL, 
                placebo_iterations = NULL, 
                folds = NULL, 
                train_split = 0.8, 
                custom_tc = FALSE, 
                assign_factors = 3,
                list_drop_vars = FALSE,
                seed = 1234){...}
```

### **Variables**

-   `data` Data object <br>
-   `model` Model selected from `caret` CRAN (Ex: 'parRF', 'adaboost') <br>
-   `outcome` Dependent variable of interest <br>
-   `predictors` Predictors of interest (defaults to all variables in `data` except `outcome`.) <br>
-   `interactions` Interaction term(s) declared as a vector separated by ',' (Ex: c('var1\*var2', 'var3:var4')) <br>
-   `drop_vars` Specific variables to drop during omission procedure (defaults to all predictors and interactions) <br>
-   `cores` Number of computing cores to allocate (defaults to one) <br>
-   `placebo_iterations` Number of placebo (shuffling) interations to run (defaults to 10) <br>
-   `folds` Number of K-Folds for `trainControl` in `caret` CRAN (defaults to 5) <br>
-   `train_split` Proportion of data for train/test split (Defaults to 0.8 -- Indicating 80/20 Split) <br>
-   `custom_tc` Custom `trainControl` parameters (For `caret` models that require unique/specific parameters) <br>
-   `assign_factors` Automatically assign levels to prescribe factor variables (Defaults to 3 Levels) <br>
-   `list_drop_vars` If `TRUE` assigns drop_vars as a group designated by object in global environment (Ex: vars = c('var1', 'var2', 'var3') and drops them collectively instead of individually. <br>
-   `seed` Random seed generator (Defaults to `1234`)

### **Johnson-Strother Replication (The Least Responsive Branch)**

```{r JS_Test, eval = F}

js_test <- pai(data = js,
               model = 'parRF',
               outcome = 'direction',
               predictors = NULL,
               interactions = NULL,
               drop_vars = drop_var_list,
               cores = 8,
               placebo_iterations = 200,
               list_drop_vars = TRUE,
               folds = 10,
               custom_tc = 'repeats = 5',
               seed = 254){...}
```


#### **Diagnostic Output Retrieval**

```{r PAI Diagnostic Function, eval = F}

pai_diagnostic_retrieval <- function(output, 
                                     diagnostic, 
                                     type, 
                                     variables = NULL, 
                                     combine_plots = FALSE){...}
```


-   `output` PAI Object (ex: `js_test`)
-   `diagnostic` PAI sequence to retrieve. Options: `push`, `placebo` (permutations), `bootstrap`, or `summary`.
-   `type` Type of diagnostic to retrieve. Options: `figure`, `all` (*placebo only*), `data`, or `distribution` (*bootstrap only*)
-   `variables` Vector of variable names to filter diagnostic (ex: `c('var2', 'var3')`). Defaults to *all*
-   `combine_plots` If `TRUE`, Returns multi-variable diagnostic figures as a single object using `cowplot` (CRAN). 


##### **Placebo Iterations**

```{r placebo figure, echo=TRUE}

pai_diagnostic_retrieval(output = js_test, 
                         diagnostic = 'placebo', 
                         type = 'all')
```

*Note*: For continuous vars, change represents change in RMSE. For Binomial terms, it represents predictive accuracy. 

##### **Bootstrap Distribution**

```{r boostrap distribution figure, echo=TRUE}

pai_diagnostic_retrieval(output = js_test, 
                         diagnostic = 'bootstrap', 
                         type = 'distribution',
                         combine_plots = TRUE)

```

##### **Summary Output**

```{r summary_output, echo=TRUE}

pai_diagnostic_retrieval(output = js_test, 
                         diagnostic = 'summary')

```
